Dense depth estimation from image pairs

### 2021-06-10 paper/paper.tex
computer vision hard

Fundamentally, dense variational methods such as \eqref{horn_schunck}, \eqref{dense_geometry} follow these same lines. First,
a cost functional of a image with continuous domain is formulated, penalizing unwanted properties of the solution. This cost functional is discretized,
and the algorithm outputs a discrete function (such as a denoised image, or a depth map, or an optical flow field) which minimizes the discrete cost function.
The majority of complexity is in the method used to minimize (or attempt to minimize) this cost function, which could be highly non-linear.
See the TUM lecture series by Cremers \ref{variational_lectures}, freely available online, for more discussion.

@@

Figures \ref{noisevis_groundtruth} and \ref{noisevis_computed} visualize the problem with this approach.
Figure \ref{noisevis_groundtruth} displays, using the the ground truth depth map data provided by the Kinect sensor \ref{tum_dataset}, anticlockwise
from the bottom right:
\begin{itemize}
    \item The reprojection image.
    \item The reprojection error.
    \item A top-down view of the depth map placed in world space.
    \item The depth map.
\end{itemize}
Figure \ref{noisevis_computed} displays the same results when using a depth map computed with the naive brute-force algorithm outlined above.
The ground truth reprojection image contains ``coloured shadows'' where the reprojection

>>>>

Fundamentally, dense variational methods such as \eqref{horn_schunck}, \eqref{dense_geometry} follow these same lines. First,
a cost functional of a image with continuous domain is formulated, penalizing unwanted properties of the solution. This cost functional is discretized,
and the algorithm outputs a discrete function (such as a denoised image, or a depth map, or an optical flow field) which minimizes the discrete cost function.
The majority of the complexity is in the method used to minimize (or attempt to minimize) this cost function, which could be highly non-linear.
See the TUM lecture series by Cremers \ref{variational_lectures}, freely available online, for more discussion.

@@

Figures \ref{noisevis_groundtruth} and \ref{noisevis_computed} visualize the problem with this approach.
Figure \ref{noisevis_groundtruth} displays, using the the ground truth depth map data provided by the Kinect sensor \ref{tum_dataset}, anticlockwise
from the bottom right:
\begin{itemize}
    \item The reprojection image.
    \item The reprojection error.
    \item A top-down view of the depth map placed in world space.
    \item The depth map.
\end{itemize}
Figure \ref{noisevis_computed} displays the same results when using a depth map computed with the naive brute-force algorithm outlined above.

The ground truth reprojection image contains ``coloured shadows'' due to occlusion. These also contribute
to high (white) values in the reprojection error image. The brute-force depth map avoids this occlusion problem.

Consider a pixel in frame 1 corresponding a point which, from the perspective of camera 2, is behind the blue die.
Likely, the line search in frame 2 will find
an unoccluded point, of similar colour, on the table. This, however, gives an unrealistic (and noisy) depth value in general --- compare
the depth images in figures \ref{noisevis_groundtruth} and \ref{noisevis_computed}. Clearly we would like to favour the depth map in
\eqref{noisevis_groundtruth}, and this is exactly the reason for the (denoising) regularizing term in \eqref{rof_continuous}.

Due to the freedom of the line search, the brute-force method has achieved low reprojection error (bottom right of figure \ref{noisevis_computed}).
With the ground truth depth map, however, the self-occlusion causes a large amount of reprojection error, which will penalize the cost function
\eqref{rof_continuous}. We would clearly like to minimize the total reprojection error (with the data term), but also keep the depth map ``smooth'' (with the regularizer term), as achieved in \ref{dense_geometry}.
However, it is difficult to choose a good value of $\lambda$ to balance the data and regularizer.

We propose a modification to the method of \ref{dense_geometry}, by removing the
